### 2016-10-20 sections/implementation.tex
Update on Overleaf.

$$\mtrx{A}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{n}}S_{n}\mtrx{V_{n}^{T}}$$

@@

$$\mtrx{A'}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{r}}S_{r}\mtrx{V_{r}^{T}}$$

@@

$$CR=\frac{r(m+n+1)}{m n}$$

@@

$$r<\frac{m n}{m+n+1}$$

@@

\todo[inline]{jak se pocita chyba; jak se da ridit maximalni chyba}

>>>>

$$\mtrx{A}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{n}}S_{n}\mtrx{V_{n}^{T}},$$

@@

$$\mtrx{A'}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{r}}S_{r}\mtrx{V_{r}^{T}}.$$

@@

$$CR=\frac{r(m+n+1)}{m n},$$

@@

$$r<\frac{m n}{m+n+1}.$$

@@

Once the SVD decomposition is calculated for the result component there are two strategies how to proceed with the compression. Each strategy is assigned a control parameter that determines resulting compression ratio or approximation error.
\begin{itemize}
\item \textbf{size} -- If the focus is only on the size of compressed data, the rank $r$ of the approximation matrix can be calculated by the formula

$$r=\ceil*{s \times \frac{m n}{m+n+1}},$$

where $s$ is the size factor, $0 \leq s \leq 1$.

\item \textbf{quality} -- Often the most important parameter to follow is the approximation error. ...

\todo[inline]{Pridat odvozeni vypoctu NRMSD ze singularnich cisel a pote postup, jak ziskat ze singularnich cisel a quality faktoru parametr r}

\end{itemize}

\todo[inline]{jak se pocita chyba; jak se da ridit maximalni chyba;}
